---
title: "projStriata2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install and load libraries, echo = F, message = F, warning = F, include=FALSE}
library(ArchR)
library(knitr)
library(tidyverse)
library(clusterProfiler)
library(org.Mm.eg.db)
library(dplyr)
library(viridis)
```

```{r set threads, message = F, warning = F, include=FALSE}
#set threads specific to your machine
addArchRThreads(threads = 22) 
```

```{r Load projStriata1, include=FALSE}
projStriata1 <- loadArchRProject(path = "./Save-ProjStriata1/")
```

```{r Filter Doublets, eval=TRUE}
# Next we can filter out putative doublets based on the scores established in the `infer doublets` chunk. Importantly, this does not delete the data from the Arrow files, but rather forces ArchRProject to ignore these cells. 
projStriata2 <- filterDoublets(projStriata1)
```

Filtering 153 cells from ArchRProject!
	Ctrl2_DEDUP : 43 of 2088 (2.1%)
	Mix1_DEDUP : 26 of 1614 (1.6%)
	Ctrl4_DEDUP : 20 of 1438 (1.4%)
	Mix4_DEDUP : 19 of 1396 (1.4%)
	Ctrl3_DEDUP : 15 of 1238 (1.2%)
	Ctrl1_DEDUP : 12 of 1119 (1.1%)
	Mix3_DEDUP : 14 of 1214 (1.2%)
	Mix2_DEDUP : 4 of 688 (0.6%)

```{r Run LSI, echo=TRUE, cache=FALSE, results='hide', message=FALSE}
# ArchR implements an iterative LSI dimensionality reduction via the addIterativeLSI() function.
projStriata2 <- addIterativeLSI(
    ArchRProj = projStriata2,
    useMatrix = "TileMatrix", 
    name = "IterativeLSI", 
    iterations = 2, 
    clusterParams = list( #See Seurat::FindClusters
        resolution = c(0.2), 
        sampleCells = 10000, 
        n.start = 10
    ), 
    varFeatures = 25000, 
    dimsToUse = 1:30
)
```

#### Clustering 
<br>
Now that we defined the most important peaks of each cell with iterative LSI, we can now cluster our cells.
```{r Dimensionality Reduction, echo=TRUE, results='hide', eval=TRUE, message = F, warning = F, cache=FALSE}
projStriata2 <- addClusters(
    input = projStriata2,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters",
    resolution = 0.8
)
```

To access these clusters we can use the $ accessor which shows the cluster ID for each single cell.
```{r Acess clusters, eval=TRUE, include=FALSE}
head(projStriata2$Clusters)
```

We can tabulate the number of cells present in each cluster:
```{r Tabulate number of cells in each cluster, include=TRUE}
table(projStriata2$Clusters)
write.table(as.data.frame(table(projStriata2$Clusters)), file="cellsPerCluster.csv", quote=F,sep=",",row.names=F)
```

##### To better understand which samples reside in which clusters, we can create a cluster confusion matrix across each sample using the confusionMatrix() function. 
<br>
```{r Confusion matrix of which samples reside in which cluster, echo=FALSE, cache=FALSE}
cM <- confusionMatrix(paste0(projStriata2$Clusters), paste0(projStriata2$Sample))
kable(cM)
write.table(as.data.frame(cM),file="cM.csv", quote=F,sep=",",row.names=TRUE)
```

```{r Confusion matrix as heatmap, eval=TRUE}
library(pheatmap)
cM <- cM / Matrix::rowSums(cM)
p <- pheatmap::pheatmap(
    mat = as.matrix(cM), 
    color = paletteContinuous("whiteBlue"), 
    border_color = "black"
)
p
```


```{r UMAP Generation and Visualization, echo=TRUE, cache=FALSE, message=FALSE, results='hide'}
projStriata2 <- addUMAP(
    ArchRProj = projStriata2, 
    reducedDims = "IterativeLSI", 
    name = "UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine"
)
```

```{r Add treatment information to sample}
projStriata2$Treatment <- plyr::revalue(projStriata2$Sample, 
                                   c('Ctrl1_DEDUP' = "Ctrl",
                                     'Ctrl2_DEDUP' = "Ctrl",
                                     'Ctrl3_DEDUP' = "Ctrl",
                                     'Ctrl4_DEDUP' = "Ctrl",
                                     'Mix1_DEDUP' = "Mix",
                                     'Mix2_DEDUP' = "Mix",
                                     'Mix3_DEDUP' = "Mix",
                                     'Mix4_DEDUP' = "Mix"
                                     ))
```


```{r UMAP Visualization, include=FALSE, eval=TRUE}
# We can visualize the UMAP in a number of ways by calling various attributes of the cells stored in the `cellColData` matrix. Here, we can visualize the UMAP by sample, or clusters.
p1 <- plotEmbedding(ArchRProj = projStriata2, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p2 <- plotEmbedding(ArchRProj = projStriata2, colorBy = "cellColData", name = "Clusters", embedding = "UMAP")
p3 <- plotEmbedding(ArchRProj = projStriata2, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p1, p2, p3, type = "h")
```

```{r Save UMAP embedding as PDF, include=FALSE, message = FALSE}
#To save an editable vectorized version of this plot, we use the plotPDF() function.
plotPDF(p1,p2, p3, name = "Plot-UMAP-Sample-Clusters.pdf",
        ArchRProj = projStriata2, addDOC = FALSE, width = 5, height = 5)
```

### Determine sample proportions in each cluster

```{r}
metadata <- projStriata2@cellColData
idxPass <- which(metadata$TSSEnrichment >= 4)
idxSample <- BiocGenerics::which(projStriata2$TSSEnrichment >= 4)
cellsSample <- projStriata2$cellNames[idxSample]
projStriata2.sub <- projStriata2[cellsSample, ]

write.table(x=table(projStriata2.sub$Sample)
            , "Number_of_cells_per_Sample_4TSSEnrichment.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = T,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r}
table(projStriata2.sub$Treatment)
table(projStriata2.sub$Clusters)
d <- data.frame(projStriata2.sub@cellColData)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), mean)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), median)

p4 <- plotEmbedding(ArchRProj = projStriata2, colorBy = "cellColData", name = "DoubletEnrichment", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata2, colorBy = "cellColData", name = "TSSEnrichment", embedding = "UMAP")
```

```{r}
plotPDF(p4,p5, name = "Plot-UMAP-DoubletEnrichment-TSSEnrichment", ArchRProj = projStriata2, addDOC = FALSE, width = 5, height = 5)
```


```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters), nrow)
names(cp) <- c("sample", "cluster", "cells")
names(cp) <- c("sample", "cluster", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=10)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:10])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp$cluster <- factor(cp$cluster,levels(cp$cluster)[c(1,3,4,5,6,7,8,9,10,2)])
levels(cp$cluster)
```

```{r}
p6 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,70))
p6 + ggsave(filename = "proportion_all.png")

p7 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p7 + ggsave(filename = "proportions.png") 
```


### Gene Scores and Marker Genes with ArchR

```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
# We'll begin by identifying marker genes using gene scores. Recall, gene scores were added when the ArchRProject was created in
addArchRThreads(threads = 1)
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata2, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon"
)
```

We can then make a list of marker genes with the desired cutoffs and list for each cluster
```{r Marker gene statistical and expression cutoff, eval=TRUE}
addArchRThreads(threads = 22)
markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= 1.25")
markerList$C2
write.table(as.data.frame(markerList),file="markerlist.csv", quote=F,sep=",",row.names=F)
```

```{r, include=FALSE, eval=TRUE}
heatmapGS <- plotMarkerHeatmap(
  seMarker = markersGS, 
  cutOff = "FDR <= 0.01 & Log2FC >= 1.25", 
  transpose = TRUE
)
```

```{r Save PDF of all marker genes, include=FALSE, eval=TRUE}
plotPDF(heatmapGS, name = "GeneScores-Marker-Heatmap", width = 8, height = 6, ArchRProj = projStriata2, addDOC = FALSE)
```

```{r load markers}
scRNAmarker <- read_csv("mmc3.csv") %>% 
  dplyr::select(-"...1")

scATACmarkers <- read_csv("markerlist.csv") %>% 
  dplyr::select("group_name", "name", "Log2FC") %>% 
  dplyr::rename("gene" = "name") %>% 
  dplyr::rename("Log2FC_atac" = "Log2FC")

scMarkers <- left_join(scRNAmarker, scATACmarkers, by = "gene") %>% 
  drop_na() %>% 
  group_by(group_name) %>% 
  arrange(desc(Log2FC_atac))
```


```{r Assign genes to clusters, message = FALSE, cache = TRUE}
#Now we can overlay our marker gene scores on our 2D UMAP embedding.
markerGenes  <- c(
    "Aqp4", "Gjb6",  #Astrocyte
    "Mog", "Aspa", #Oligodentrocyte
    "Flt1", #Vascular cells
    "Cx3cr1", "Tmem119", "Tgfbr1", "Ccl4", #Immune Cells
    "Pdgfra", #Stem Cells
    "Dlx1", #Stem cells
    "Prlr", "Slc4a5","Tmem72", #Ependy sec
    "Tmem212", #Ependy cilia
    "Mrc1", #Immune cells
    "Trank1", "Atp1a3", "Rgs9" #Neurons
    )

heatmapGS <- plotMarkerHeatmap(
  seMarker = markersGS, 
  cutOff = "FDR <= 0.01 & Log2FC >= 1.25", 
  labelMarkers = markerGenes,
  transpose = TRUE
)
```

```{r Save PDF of heat map of all marker genes}
plotPDF(heatmapGS, name = "GeneScores-Marker-Heatmap", width = 8, height = 6, ArchRProj = projStriata2, addDOC = FALSE)
```

```{r Assign genes to clusters, message = FALSE, cache = TRUE}
#Now we can overlay our marker gene scores on our 2D UMAP embedding.
##These are marker genes pulled from the scMarker table + scRNA paper
markerGenes  <- c(
    "Aqp4",  #Astrocyte
    "Mog", #Oligodentrocyte
    "Flt1", #Vascular cells
    "Cx3cr1", "Tgfbr1", #Immune Cells
    "Pdgfra", #Stem Cells
    "Dlx1", #Stem cells
    "Tmem72", #Ependy sec
    "Tmem212", #Ependy cilia
    "Mrc1", #Immune cells
    "Trank1" #Neurons
    )

p8 <- plotEmbedding(
    ArchRProj = projStriata2, 
    colorBy = "GeneScoreMatrix", 
    name = markerGenes, 
    embedding = "UMAP",
    quantCut = c(0.01, 0.95),
    imputeWeights = NULL
)
```

```{r Plot UMAP Marker Genes}
#To plot a specific gene we can subset this plot list using the gene name.
p8$Trank1

#Plot all genes defined in markerGenes
p9 <- lapply(p8, function(x){
    x + guides(color = FALSE, fill = FALSE) + 
    theme_ArchR(baseSize = 6.5) +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +
    theme(
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()
    )
})
do.call(cowplot::plot_grid, c(list(ncol = 3),p2))
```
<br>


```{r, message=FALSE}
#Save an editable PDF version
plotPDF(plotList = p8, 
    name = "Plot-UMAP-Marker-Genes-WO-Imputation.pdf", 
    ArchRProj = projStriata2, 
    addDOC = FALSE, width = 5, height = 5)
```
<br>

### Marker Genes Imputation with MAGIC

```{r}
projStriata2 <- addImputeWeights(projStriata2)
```

```{r}
markerGenes  <- c(
    "Aqp4",  #Astrocyte
    "Mog", #Oligodentrocyte
    "Flt1", #Vascular cells
    "Cx3cr1", #Immune Cells
    "Pdgfra", #Stem Cells
    "Dlx1", #Stem cells
    "Tmem72", #Ependy sec
    "Tmem212", #Ependy cilia
    "Mrc1", #Immune cells
    "Trank1" #Neurons
    )

p <- plotEmbedding(
    ArchRProj = projStriata2, 
    colorBy = "GeneScoreMatrix", 
    name = markerGenes, 
    embedding = "UMAP",
    imputeWeights = getImputeWeights(projStriata2)
)
```

```{r}
#Rearrange for grid plotting
p2 <- lapply(p, function(x){
    x + guides(color = FALSE, fill = FALSE) + 
    theme_ArchR(baseSize = 6.5) +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +
    theme(
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()
    )
})
do.call(cowplot::plot_grid, c(list(ncol = 3),p2))
```

```{r All possible marker genes with imputed gene score}
markerGenes  <- c(
    "Aqp4", "Gjb6", #Astrocyte
    "Mog", "Aspa", #Oligodentrocyte
    "Nfasc", #Newly formed oligodendrocytes NFOs
    "Klk6", # Mature Oligodendrocytes
    "Flt1", #Vascular cells
    "Cx3cr1", "Tmem119", "Olfml3", "Mlxipl", #Immune Cells and Microglia
    "Mrc1", # Perivascular Macrophages
    "Pdgfra", #Stem Cells
    "Dlx1", #Stem cells
    "A930009A15Rik", # OPC (oligodendrocyte precursor cells)
    "Tmem72", "Prlr", "Slc4a5", #Ependy sec
    "Tmem212", #Ependy cilia
    "Mrc1", #Immune cells
    "Trank1", "Atp1a3" #Neurons
    )

p3 <- plotEmbedding(
    ArchRProj = projStriata2, 
    colorBy = "GeneScoreMatrix", 
    name = markerGenes, 
    embedding = "UMAP",
    imputeWeights = getImputeWeights(projStriata2)
)
```

```{r}
p3$Slc4a5
plotPDF(plotList = p3, 
    name = "Plot-UMAP-All-Marker-Genes-W-Imputation.pdf", 
    ArchRProj = projStriata2, 
    addDOC = FALSE, width = 5, height = 5)
```

```{r}
#Rearrange for grid plotting
p4 <- lapply(p3, function(x){
    x + guides(color = FALSE, fill = FALSE) + 
    theme_ArchR(baseSize = 6.5) +
    theme(plot.margin = unit(c(0, 0, 0, 0), "cm")) +
    theme(
        axis.text.x=element_blank(), 
        axis.ticks.x=element_blank(), 
        axis.text.y=element_blank(), 
        axis.ticks.y=element_blank()
    )
})
do.call(cowplot::plot_grid, c(list(ncol = 3),p4))
```

```{r Tfs and splicing genes}
markerGenes  <- c(
    "Sox9", # Astrocyte
    "Mlxipl", # Immune Cells and Microglia
    "Foxj1" # Ependy cilia
    )

p5 <- plotEmbedding(
    ArchRProj = projStriata2, 
    colorBy = "GeneScoreMatrix", 
    name = markerGenes, 
    embedding = "UMAP",
    imputeWeights = getImputeWeights(projStriata2)
)
```

```{r}
p5$Sox9
plotPDF(plotList = p5, 
    name = "Plot-UMAP-TF-Marker-Genes-W-Imputation.pdf", 
    ArchRProj = projStriata2, 
    addDOC = FALSE, width = 5, height = 5)
```


### GO and KEGG analysis

```{r}
markerList$C1$cluster <- "C1"
markerList$C2$cluster <- "C2"
markerList$C3$cluster <- "C3"
markerList$C4$cluster <- "C4"
markerList$C5$cluster <- "C5"
markerList$C6$cluster <- "C6"
markerList$C7$cluster <- "C7"
markerList$C8$cluster <- "C8"
markerList$C9$cluster <- "C9"
markerList$C10$cluster <- "C10"
markers <- rbind(markerList$C1,
                 markerList$C2,
                 markerList$C3,
                 markerList$C4,
                 markerList$C5,
                 markerList$C6,
                 markerList$C7,
                 markerList$C8,
                 markerList$C9,
                 markerList$C10)
write.table(x=markers, "marker_genes.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = FALSE,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")

```

```{r}
markers <- read.table("marker_genes.txt", header = TRUE)
geneid <- markers$name
markers$entrezid <- AnnotationDbi::select(org.Mm.eg.db, keys=geneid, columns="ENTREZID", 
                                          keytype="SYMBOL")
clusterprofilerlist<-list("C1"=subset(markers$entrezid$ENTREZID, markers$cluster =="C1")[1:100], 
                          # you can use all DA genes in one cluster or set number
                          # here I only take top 100 genes for each cluster [1:100]
                          "C2"=subset(markers$entrezid$ENTREZID, markers$cluster =="C2")[1:100],
                          "C3"=subset(markers$entrezid$ENTREZID, markers$cluster =="C3")[1:100],
                          "C4"=subset(markers$entrezid$ENTREZID, markers$cluster =="C4")[1:100],
                          "C5"=subset(markers$entrezid$ENTREZID, markers$cluster =="C5")[1:100],
                          "C6"=subset(markers$entrezid$ENTREZID, markers$cluster =="C6")[1:100],
                          "C7"=subset(markers$entrezid$ENTREZID, markers$cluster =="C7")[1:100],
                          "C8"=subset(markers$entrezid$ENTREZID, markers$cluster =="C8")[1:100],
                          "C9"=subset(markers$entrezid$ENTREZID, markers$cluster =="C9")[1:100],
                          "C10"=subset(markers$entrezid$ENTREZID, markers$cluster =="C10")[1:100]
)
```

```{r}
cc_go <- clusterProfiler::compareCluster(geneClusters = clusterprofilerlist,
                                         fun = "enrichGO", 
                                         OrgDb= org.Mm.eg.db, 
                                         ont= "BP", 
                                         pvalueCutoff=0.05, 
                                         pAdjustMethod='BH')
dotplot(cc_go, showCategory = 5) + scale_color_viridis(direction = -1, trans = "log10")
```

```{r}
png("cc_go.png", height = 10, width = 20, units = "in", res = 600)
dotplot(cc_go, showCategory = 5) + scale_color_viridis(direction = -1, trans = "log10")
dev.off() 
```
```{r}
cc_gos <- clusterProfiler::simplify(cc_go, cutoff=0.05, by= "p.adjust")
dotplot(cc_gos, showCategory = 5) +scale_color_viridis(direction = -1, trans = "log10")
```
```{r}
png("cc_gos.png", height = 10, width = 20, units = "in", res = 600)
dotplot(cc_gos, showCategory = 5) +scale_color_viridis(direction = -1, trans = "log10")
dev.off() 
```


```{r}
cp <- ddply(projStriata2@cellColData, .(projStriata2@cellColData$Sample, projStriata2@cellColData$Clusters), nrow)
names(cp) <- c("sample", "cluster", "cells")
```


```{r Save ArchRProject}
saveArchRProject(ArchRProj = projStriata2, outputDirectory = "Save-ProjStriata2", load = FALSE)
```


