---
title: "Macrophages and microglia analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install and load libraries, echo = F, message = F, warning = F, include=FALSE}
library(ArchR)
library(knitr)
library(tidyverse)
library(clusterProfiler)
library(org.Mm.eg.db)
library(dplyr)
library(viridis)
library(ggpubr)
```

```{r set threads, message = F, warning = F, include=FALSE}
#set threads specific to your machine
addArchRThreads(threads = 22) 
```

```{r}
projStriata4 <- loadArchRProject(path = "./Save-ProjStriata4/")
projStriata.glia <- loadArchRProject(path = "./GliaSubset/")
```

## Pairwise using entire dataset

```{r}
clusterxtrt <- paste0(projStriata4$Clusters2, "_", projStriata4$Treatment)
projStriata4$clusterxtrt <- clusterxtrt
markerTest <- getMarkerFeatures(
  ArchRProj = projStriata4, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "Macrophages and Microglia_Mix",
  bgdGroups = "Macrophages and Microglia_Ctrl"
)
```

```{r}
pma <- plotMarkers(seMarker = markerTest, name = "Macrophages and Microglia_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma
```

```{r}
pv <- plotMarkers(seMarker = markerTest, name = "Macrophages and Microglia_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv
```

```{r}
metadata <- as.data.frame(getCellColData(ArchRProj = projStriata4))
glia <- rownames(metadata[metadata$Clusters2 == "Macrophages and Microglia",])

projStriata.glia <- subsetArchRProject(
  ArchRProj = projStriata4,
  cells = glia,
  outputDirectory = "GliaSubset",
  dropCells = TRUE,
  logFile = NULL,
  threads = getArchRThreads(),
  force = TRUE
)
```

```{r}
plotPDF(pma, pv, name = "Macrophages-Microglia-GeneScoreMatrix-Mix-vs-Ctrl", width = 5, height = 5, ArchRProj = projStriata.glia, addDOC = FALSE)
```


```{r}
markerTest.glia <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "Treatment",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "Mix",
  bgdGroups = "Ctrl"
)
```

```{r}
pma2 <- plotMarkers(seMarker = markerTest.glia, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma2
```

```{r}
pv2 <- plotMarkers(seMarker = markerTest.glia, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv2
```


## Subcluster analyses

### Resolution .4 = three subclusters

```{r}
projStriata.glia <- addClusters(
    input = projStriata.glia,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters3",
    resolution = 0.4,
    force = TRUE
)
```

```{r}
head(projStriata.glia$Clusters3)
table(projStriata.glia$Clusters3)
cM <- confusionMatrix(paste0(projStriata.glia$Sample), paste0(projStriata.glia$Clusters3))
cM
```

```{r}
projStriata.glia <- addUMAP(
    ArchRProj = projStriata.glia, 
    reducedDims = "IterativeLSI", 
    name = "UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine",
    force = TRUE
)
```

```{r}
p1 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p2 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Clusters3", embedding = "UMAP")
p3 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p1, p2, p3, type = "h")
```

```{r}
plotPDF(p1,p2, p3, name = "Plot-UMAP-Glia-subcluster-threeclusters.pdf", ArchRProj = projStriata.glia, addDOC = FALSE, width = 5, height = 5)
```


```{r}
metadata.4 <- projStriata.glia@cellColData
idxPass <- which(metadata.4$TSSEnrichment >= 4)
idxSample <- BiocGenerics::which(projStriata.glia$TSSEnrichment >= 4)
cellsSample <- projStriata.glia$cellNames[idxSample]
projStriata.glia.sub <- projStriata.glia[cellsSample, ]

write.table(x=table(projStriata.glia.sub$Sample)
            , "./GliaSubset/glia_4TSSEnrichment-threeclusters.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = T,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r}
table(projStriata.glia$Treatment)
table(projStriata.glia$Clusters3)
write.table(table(projStriata.glia$Treatment), 
            file = "./GliaSubset/glia-by-treatment-res.4.csv", 
            quote=F,
            sep=",",
            row.names=F)

d <- data.frame(projStriata.glia.sub@cellColData)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), mean)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), median)

p4 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "DoubletEnrichment", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "TSSEnrichment", embedding = "UMAP")
```

```{r}
plotPDF(p4,p5, name = "Plot-UMAP-Glia-DoubletEnrichment-TSSEnrichment-res.4", ArchRProj = projStriata.glia, addDOC = FALSE, width = 5, height = 5)
```

### Find proportions

```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters3, d$Treatment), nrow)
names(cp) <- c("sample", "cluster", "treatment", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=3)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:3])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp <- cp %>% 
  unite(grouping, c(cluster, treatment), remove = FALSE)
```

```{r}
p1 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,80))
p1
p1 + ggsave(filename = "./GliaSubset/proportion_all-threeclusters.png")

p2 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p2 + stat_compare_means(aes(group = group2), method = "t.test", label="p.signif", hide.ns = FALSE) + ggsave(filename = "./GliaSubset/proportions-treatment-threeclusters.png") 
```
### Marker Identification 
```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
# We'll begin by identifying marker genes using gene scores. Recall, gene scores were added when the ArchRProject was created in
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata.glia, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters3",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList1 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList1$C3
write.table(as.data.frame(markerList1),file="./GliaSubset/markerlist-glia-threeclusters.csv", quote=F,sep=",",row.names=F)
```

### Pairwise testing for three subclusters under .4 resolution

#### C1 analysis
```{r}
clusterxtrt <- paste0(projStriata.glia$Clusters3, "_", projStriata.glia$Treatment)
projStriata.glia$clusterxtrt <- clusterxtrt
markerTest1 <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```

```{r}
pma1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma1
```

```{r}
pv1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv1
```

```{r}
plotPDF(pma1, pv1, name = "C1-Mix-vs-Ctrl-GeneScoreMatrix-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata.glia, addDOC = FALSE)
```

#### C2 analysis

```{r}
markerTest2 <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma2
```

```{r}
pv2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv2
```

```{r}
plotPDF(pma2, pv2, name = "C2-Mix-vs-Ctrl-GeneScoreMatrix-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata.glia, addDOC = FALSE)
```

#### C3 analysis
```{r}
markerTest1 <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C3_Mix",
  bgdGroups = "C3_Ctrl"
)
```

```{r}
pma3 <- plotMarkers(seMarker = markerTest3, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma3
```

```{r}
pv3 <- plotMarkers(seMarker = markerTest3, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv3
```

```{r}
plotPDF(pma3, pv3, name = "C3-Mix-vs-Ctrl-GeneScoreMatrix-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata.glia, addDOC = FALSE)
```

### Resolution .1 = two subclusters

```{r}
projStriata.glia <- addClusters(
    input = projStriata.glia,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters4",
    resolution = 0.1,
    force = TRUE
)
```

```{r}
head(projStriata.glia$Clusters4)
table(projStriata.glia$Clusters4)
cM <- confusionMatrix(paste0(projStriata.glia$Sample), paste0(projStriata.glia$Clusters4))
cM
```

```{r}
p4 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Clusters4", embedding = "UMAP")
p6 <- plotEmbedding(ArchRProj = projStriata.glia, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p4, p5, p6, type = "h")
```

```{r}
plotPDF(p1,p2, p3, name = "Plot-UMAP-Glia-subcluster-threeclusters.pdf", ArchRProj = projStriata.glia, addDOC = FALSE, width = 5, height = 5)
```

### Find proportions of 2 clusters

```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters4, d$Treatment), nrow)
names(cp) <- c("sample", "cluster", "treatment", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=2)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:2])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp <- cp %>% 
  unite(grouping, c(cluster, treatment), remove = FALSE)
```

```{r}
p3 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,80))
p3
p3 + ggsave(filename = "./GliaSubset/proportion_all-twoclusters.png")

p4 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p4 + stat_compare_means(aes(group = group2), method = "t.test", label="p.signif", hide.ns = FALSE) + ggsave(filename = "./GliaSubset/proportions-treatment-twoclusters.png") 
```

### Marker Identification 
```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
# We'll begin by identifying marker genes using gene scores. Recall, gene scores were added when the ArchRProject was created in
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata.glia, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters4",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList2 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList2$C2
write.table(as.data.frame(markerList2),file="./GliaSubset/markerlist-glia-twoclusters.csv", quote=F,sep=",",row.names=F)
```

### Pairwise testing for two subclusters under .1 resolution

#### C1 analysis
```{r}
clusterxtrt <- paste0(projStriata.glia$Clusters4, "_", projStriata.glia$Treatment)
projStriata.glia$clusterxtrt <- clusterxtrt
markerTest4 <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```

```{r}
pma4 <- plotMarkers(seMarker = markerTest4, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma4
```

```{r}
pv4 <- plotMarkers(seMarker = markerTest4, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv4
```

#### C1 analysis
```{r}
markerTest5 <- getMarkerFeatures(
  ArchRProj = projStriata.glia, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma5 <- plotMarkers(seMarker = markerTest5, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma5
```

```{r}
pv5 <- plotMarkers(seMarker = markerTest5, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv5
```

```{r}
plotPDF(pma5, pv5, name = "C2-Mix-vs-Ctrl-GeneScoreMatrix-MA-Volcano-twosubclusters", width = 5, height = 5, ArchRProj = projStriata.glia, addDOC = FALSE)
```

```{r}
saveArchRProject(ArchRProj = projStriata.glia, outputDirectory = "GliaSubset/", load = FALSE)
```

