---
title: "Neuron subcluster analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r install and load libraries, echo = F, message = F, warning = F, include=FALSE}
library(ArchR)
library(knitr)
library(tidyverse)
library(clusterProfiler)
library(org.Mm.eg.db)
library(dplyr)
library(viridis)
library(ggpubr)
```

```{r set threads, message = F, warning = F, include=FALSE}
#set threads specific to your machine
addArchRThreads(threads = 22) 
```

```{r Load projStriata1, include=FALSE}
projStriata3 <- loadArchRProject(path = "./Save-ProjStriata3/")
projStriata4 <- loadArchRProject(path = "./Save-ProjStriata4/")
projStriata5 <- loadArchRProject(path = "./NeuronSubset/")
```
### Pairwise without subclustering: Seoyeon's method

```{r}
clusterxtrt <- paste0(projStriata4$Clusters2, "_", projStriata4$Treatment)
projStriata4$clusterxtrt <- clusterxtrt
markerTest <- getMarkerFeatures(
  ArchRProj = projStriata4, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "Neurons_Mix",
  bgdGroups = "Neurons_Ctrl"
)
```

```{r}
pma <- plotMarkers(seMarker = markerTest, name = "Neurons_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma
```

```{r}
pv <- plotMarkers(seMarker = markerTest, name = "Neurons_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv
```

```{r}
plotPDF(pma, pv, name = "Neurons-GeneScoreMatrix-Mix-vs-Ctrl", width = 5, height = 5, ArchRProj = projStriata4, addDOC = FALSE)
```

```{r}
projStriata4 <- addPeakMatrix(projStriata3)
getAvailableMatrices(projStriata4)
```

```{r}
#Our scRNA labels
table(projStriata4$Clusters2)
```


```{r}
metadata <- as.data.frame(getCellColData(ArchRProj = projStriata4))
neuron_cells <- rownames(metadata[metadata$Clusters2 == "Neurons",])

projStriata5 <- subsetArchRProject(
  ArchRProj = projStriata4,
  cells = neuron_cells,
  outputDirectory = "NeuronSubset",
  dropCells = TRUE,
  logFile = NULL,
  threads = getArchRThreads(),
  force = TRUE
)
```

```{r}
clusterxtrt <- paste0(projStriata5$Clusters2, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "Treatment",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "Mix",
  bgdGroups = "Ctrl"
)
```

```{r}
pma <- plotMarkers(seMarker = markerTest, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma
```

```{r}
pv <- plotMarkers(seMarker = markerTest, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv
```

### Markerlist for subset neurons by treatment 

```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Treatment",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList$Mix
write.table(as.data.frame(markerList),file="./NeuronSubset/markerlist-subsetNeurons-by-treatment.csv", quote=F,sep=",",row.names=F)
```

## Subclustering Analyses

### Resolution 0.4 - Two cluster analysis

```{r}
projStriata5 <- addClusters(
    input = projStriata5,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters3",
    resolution = 0.4,
    force = TRUE
)
```

```{r}
head(projStriata5$Clusters3)
table(projStriata5$Clusters3)
cM <- confusionMatrix(paste0(projStriata5$Sample), paste0(projStriata5$Clusters3))
cM
```

```{r}
library(pheatmap)
cM <- cM / Matrix::rowSums(cM)
p <- pheatmap::pheatmap(
    mat = as.matrix(cM), 
    color = paletteContinuous("whiteBlue"), 
    border_color = "black"
)
p
```

```{r}
projStriata5 <- addUMAP(
    ArchRProj = projStriata5, 
    reducedDims = "IterativeLSI", 
    name = "UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine",
    force = TRUE
)
```

```{r}
p1 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p2 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Clusters3", embedding = "UMAP")
p3 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p1, p2, p3, type = "h")
```

```{r}
plotPDF(p1,p2, p3, name = "Plot-UMAP-Neuron-subcluster-twoclusters.pdf", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```


```{r}
metadata <- projStriata5@cellColData
idxPass <- which(metadata$TSSEnrichment >= 4)
idxSample <- BiocGenerics::which(projStriata5$TSSEnrichment >= 4)
cellsSample <- projStriata5$cellNames[idxSample]
projStriata5.sub <- projStriata5[cellsSample, ]

write.table(x=table(projStriata5.sub$Sample)
            , "./NeuronSubset/Neuron_subcluster_4TSSEnrichment_twosubclusters.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = T,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r}
table(projStriata5.sub$Treatment)
table(projStriata5.sub$Clusters3)
write.table(table(projStriata5.sub$Treatment), 
            file = "./NeuronSubset/Neurons-by-treatment-res.5.csv", 
            quote=F,
            sep=",",
            row.names=F)

d <- data.frame(projStriata5.sub@cellColData)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), mean)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), median)

p4 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "DoubletEnrichment", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "TSSEnrichment", embedding = "UMAP")
```

```{r}
plotPDF(p4,p5, name = "Plot-UMAP-Neuron-DoubletEnrichment-TSSEnrichment", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```
### Find Proportions

```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters3, d$Treatment), nrow)
names(cp) <- c("sample", "cluster", "treatment", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=2)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:2])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp <- cp %>% 
  unite(grouping, c(cluster, treatment), remove = FALSE)
```

```{r}
p6 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,80))
p6
p6 + ggsave(filename = "./NeuronSubset/Neuron-proportion-all-twoclusters.png")

p7 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p7 + stat_compare_means(aes(group = group2), method = "t.test", label="p.signif", hide.ns = FALSE) + ggsave(filename = "./NeuronSubset/Neuron-proportions-by-treatment-twoclusters.png") 
```

### Marker Identification 

```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters3",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList1 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList1$C1
write.table(as.data.frame(markerList1),file="./NeuronSubset/markerlist-neuons-twoclusters.csv", quote = F, sep = ",", row.names = F)
```

### Pairwise testing for two subclusters under .4 resolution

#### C1 analysis
```{r}
clusterxtrt <- paste0(projStriata5$Clusters3, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest1 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```
#### C1 Mix vs Ctrl
```{r}
pma1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma1
```

```{r}
pv1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv1
```

```{r}
plotPDF(pma1, pv1, name = "C1-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-twosubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```
#### C2 Mix vs Ctrl
```{r}
markerTest2 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma2
```

```{r}
pv2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv2
```


```{r}
plotPDF(pma2, pv2, name = "C2-Mix-vs-Ctrl-PeakMatrix-Markers-MA-Volcano-twosubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```
### Resolution 0.8 - Three cluster analysis

```{r}
projStriata5 <- addClusters(
    input = projStriata5,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters4",
    resolution = 0.8,
    force = TRUE
)
```

```{r}
head(projStriata5$Clusters4)
table(projStriata5$Clusters4)
cM <- confusionMatrix(paste0(projStriata5$Sample), paste0(projStriata5$Clusters4))
cM
```

.5

             C2  C1  C3
Ctrl2_DEDUP 175 288 264
Mix1_DEDUP  171 281 260
Ctrl4_DEDUP 138 204 296
Mix4_DEDUP  107 224 348
Ctrl3_DEDUP  56 191 187
Ctrl1_DEDUP  71 180 202
Mix3_DEDUP   71 226 270
Mix2_DEDUP   39 132 189

  C1   C2 
1176 3394 

.7 res 
 C1   C2 
1004 3566

```{r}
library(pheatmap)
cM <- cM / Matrix::rowSums(cM)
p <- pheatmap::pheatmap(
    mat = as.matrix(cM), 
    color = paletteContinuous("whiteBlue"), 
    border_color = "black"
)
p
```

```{r}
projStriata5 <- addUMAP(
    ArchRProj = projStriata5, 
    reducedDims = "IterativeLSI", 
    name = "UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine",
    force = TRUE
)
```

```{r}
p1 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p2 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Clusters4", embedding = "UMAP")
p3 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p1, p2, p3, type = "h")
```

```{r}
plotPDF(p1, p2, p3, name = "Plot-UMAP-Neuron-subcluster-threeclusters.pdf", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```


```{r}
metadata <- projStriata5@cellColData
idxPass <- which(metadata$TSSEnrichment >= 4)
idxSample <- BiocGenerics::which(projStriata5$TSSEnrichment >= 4)
cellsSample <- projStriata5$cellNames[idxSample]
projStriata5.sub <- projStriata5[cellsSample, ]

write.table(x=table(projStriata5.sub$Sample)
            , "./NeuronSubset/Neuron_subcluster_4TSSEnrichment_threesubclusters.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = T,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r}
table(projStriata5.sub$Treatment)
table(projStriata5.sub$Clusters4)
write.table(table(projStriata5.sub$Treatment), 
            file = "Neurons-by-treatment-threesubclusters.csv", 
            quote=F,
            sep=",",
            row.names=F)

d <- data.frame(projStriata5.sub@cellColData)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), mean)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), median)

p4 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "DoubletEnrichment", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "TSSEnrichment", embedding = "UMAP")
```

```{r}
plotPDF(p4,p5, name = "Plot-UMAP-Neuron-DoubletEnrichment-TSSEnrichment-threesubclusters", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```

### Find proportions

```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters4, d$Treatment), nrow)
names(cp) <- c("sample", "cluster", "treatment", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=3)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:3])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp <- cp %>% 
  unite(grouping, c(cluster, treatment), remove = FALSE)
```

```{r}
p6 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,70))

p6 + ggsave(filename = "./NeuronSubset/proportion_all_threeclusters.png")

p7 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p7 + stat_compare_means(aes(group = group2), method = "t.test", label="p.signif", hide.ns = FALSE) + ggsave(filename = "./NeuronSubset/proportions_treatment_threeclusters.png") 
```

### Marker Identification 
```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters4",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList1 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList1$C3
write.table(as.data.frame(markerList1),file="./NeuronSubset/markerlist-neurons-threeclusters.csv", quote = F, sep = ",", row.names = F)
```

### Pairwise Testing for the three subclusters under .8 resolution
#### C1 Mix vs Ctrl

```{r}
clusterxtrt <- paste0(projStriata5$Clusters4, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest6 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```


```{r}
pma6 <- plotMarkers(seMarker = markerTest6, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma6
```

```{r}
pv6 <- plotMarkers(seMarker = markerTest6, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv6
```

```{r}
plotPDF(pma6, pv6, name = "C1-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C2 Mix vs Ctrl

```{r}
markerTest7 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma7 <- plotMarkers(seMarker = markerTest7, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma7
```

```{r}
pv7 <- plotMarkers(seMarker = markerTest7, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv7
```

```{r}
plotPDF(pma7, pv7, name = "C2-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C3 Mix vs Ctrl analysis

```{r}
markerTest8 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C3_Mix",
  bgdGroups = "C3_Ctrl"
)
```

```{r}
pma8 <- plotMarkers(seMarker = markerTest8, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma8
```

```{r}
pv8 <- plotMarkers(seMarker = markerTest8, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv8
```

```{r}
plotPDF(pma8, pv8, name = "C3-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

### Resolution 0.95 - Four cluster analysis

```{r}
projStriata5 <- addClusters(
    input = projStriata5,
    reducedDims = "IterativeLSI",
    method = "Seurat",
    name = "Clusters5",
    resolution = .95,
    force = TRUE
)
```

```{r}
head(projStriata5$Clusters5)
table(projStriata5$Clusters5)
cM <- confusionMatrix(paste0(projStriata5$Sample), paste0(projStriata5$Clusters5))
cM
```

```{r}
library(pheatmap)
cM <- cM / Matrix::rowSums(cM)
p <- pheatmap::pheatmap(
    mat = as.matrix(cM), 
    color = paletteContinuous("whiteBlue"), 
    border_color = "black"
)
p
```

```{r}
projStriata5 <- addUMAP(
    ArchRProj = projStriata5, 
    reducedDims = "IterativeLSI", 
    name = "UMAP", 
    nNeighbors = 30, 
    minDist = 0.5, 
    metric = "cosine",
    force = TRUE
)
```

```{r}
p1 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Sample", embedding = "UMAP")
p2 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Clusters5", embedding = "UMAP")
p3 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "Treatment", embedding = "UMAP")
ggAlignPlots(p1, p2, p3, type = "h")
```

```{r}
plotPDF(p1,p2, p3, name = "Plot-UMAP-Neuron-subcluster-fourclusters.pdf", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```


```{r}
metadata <- projStriata5@cellColData
idxPass <- which(metadata$TSSEnrichment >= 4)
idxSample <- BiocGenerics::which(projStriata5$TSSEnrichment >= 4)
cellsSample <- projStriata5$cellNames[idxSample]
projStriata5.sub <- projStriata5[cellsSample, ]

write.table(x=table(projStriata5.sub$Sample)
            , "Neuron_subcluster_4TSSEnrichment_fourcluster.txt", append = FALSE, quote = FALSE, sep = "\t",
            eol = "\n", na = "NA", dec = ".", row.names = T,
            col.names = TRUE, qmethod = c("escape", "double"),
            fileEncoding = "")
```

```{r}
table(projStriata5.sub$Treatment)
table(projStriata5.sub$Clusters5)
write.table(table(projStriata5.sub$Treatment), 
            file = "Neurons-by-treatment-res.8.csv", 
            quote=F,
            sep=",",
            row.names=F)

d <- data.frame(projStriata5.sub@cellColData)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), mean)
aggregate(d[, c("nFrags","TSSEnrichment")], list(d$Treatment), median)

p4 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "DoubletEnrichment", embedding = "UMAP")
p5 <- plotEmbedding(ArchRProj = projStriata5, colorBy = "cellColData", name = "TSSEnrichment", embedding = "UMAP")
```

```{r}
plotPDF(p4,p5, name = "Plot-UMAP-Neuron-DoubletEnrichment-TSSEnrichment", ArchRProj = projStriata5, addDOC = FALSE, width = 5, height = 5)
```

```{r}
library(plyr)
cp <- ddply(d, .(d$Sample, d$Clusters5, d$Treatment), nrow)
names(cp) <- c("sample", "cluster", "treatment", "cells")

table(cp$sample) 

# put # of clusters to each = 
cells_per_sample <-rep(table(d$Sample),each=4)

# this should be the same
length(cp$sample)
length(cells_per_sample)

cp$ratio <- as.numeric(cp$cells)/cells_per_sample
sum(cp$ratio[1:4])

cp$group <- cp$sample
cp$group2 <- gsub("[0-9]_DEDUP", "",cp$group)
cp$proportion <- cp$ratio*100

cp$cluster <- factor(cp$cluster)
levels(cp$cluster)
cp <- cp %>% 
  unite(grouping, c(cluster, treatment), remove = FALSE)
```

```{r}
p6 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group)) +
    geom_bar(stat = "identity", color = "black",
           position = position_dodge()) +
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE", "#4393C3","#2166AC", "#F4A582", "#D6604D","#B2182B", "#7FCDBB"
)) +ylim(c(0,70))

p6 + ggsave(filename = "./NeuronSubset/proportion_all-fourclusters.png")

p7 <- ggplot(cp, aes(x = cluster, y = proportion, fill = group2)) +
  geom_boxplot() +
  geom_point(shape = 21, position = position_jitterdodge(jitter.width = 0), size = 0.2) + 
  theme_classic() +
  scale_fill_manual(values=c("#BABABA", "#92C5DE"))

p7 + stat_compare_means(aes(group = group2), method = "t.test", label="p.signif") + ggsave(filename = "./NeuronSubset/proportions-treatment-fourclusters.png") 
```

```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "GeneScoreMatrix", 
    groupBy = "Clusters5",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList$C1
write.table(as.data.frame(markerList),file="markerlist_neuron_res-fourclusters.csv", quote=F,sep=",",row.names=F)
```

### Pairwise Testing for the four subclusters under .95 resolution
#### C1 Mix vs Ctrl

```{r}
clusterxtrt <- paste0(projStriata5$Clusters5, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest9 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```


```{r}
pma9 <- plotMarkers(seMarker = markerTest9, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma9
```

```{r}
pv9 <- plotMarkers(seMarker = markerTest9, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv9
```

```{r}
plotPDF(pma9, pv9, name = "C1-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-foursubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C2 Mix vs Ctrl

```{r}
markerTest10 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma10 <- plotMarkers(seMarker = markerTest10, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma10
```

```{r}
pv10 <- plotMarkers(seMarker = markerTest10, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv10
```

```{r}
plotPDF(pma10, pv10, name = "C2-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-foursubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C3 Mix vs Ctrl analysis

```{r}
markerTest11 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C3_Mix",
  bgdGroups = "C3_Ctrl"
)
```

```{r}
pma11 <- plotMarkers(seMarker = markerTest11, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma11
```

```{r}
pv11 <- plotMarkers(seMarker = markerTest8, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv11
```

```{r}
plotPDF(pma11, pv11, name = "C3-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-foursubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C4 Mix vs Ctrl

```{r}
markerTest12 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "GeneScoreMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C4_Mix",
  bgdGroups = "C4_Ctrl"
)
```

```{r}
pma12 <- plotMarkers(seMarker = markerTest12, name = "C4_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma12
```

```{r}
pv12 <- plotMarkers(seMarker = markerTest12, name = "C4_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv12
```

```{r}
plotPDF(pma12, pv12, name = "C4-Mix-vs-Ctrl-GeneScoreMatrix-Markers-MA-Volcano-foursubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

## Neuron analysis using Peak Matrix

### Pairwise Testing by Treatment

```{r Marker identificiation by treatment using peak matrix}
getAvailableMatrices(projStriata5)
table(projStriata5$Treatment)

markerTest <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "Treatment",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "Mix",
  bgdGroups = "Ctrl"
)
```

```{r}
pma <- plotMarkers(seMarker = markerTest, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma
```

```{r}
pv <- plotMarkers(seMarker = markerTest, name = "Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv
```

```{r}
plotPDF(pma, pv, name = "Neurons-PeakMatrix-Mix-vs-Ctrl", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

### Marker Identification 

```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
table(projStriata5$Clusters3)

markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "PeakMatrix", 
    groupBy = "Clusters3",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList1 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList1$C2
write.table(as.data.frame(markerList1),file="./NeuronSubset/markerlist-byPeaks-neurons-twoclusters.csv", quote = F, sep = ",", row.names = F)
```

### Pairwise testing for two subclusters under .4 resolution

#### C1 analysis
```{r}
clusterxtrt <- paste0(projStriata5$Clusters3, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest1 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```

#### C1 Mix vs Ctrl

```{r}
pma1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma1
```

```{r}
pv1 <- plotMarkers(seMarker = markerTest1, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv1
```

```{r}
plotPDF(pma1, pv1, name = "C1-Mix-vs-Ctrl-PeakMatrix-Markers-MA-Volcano-twosubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C2 Mix vs Ctrl

```{r}
markerTest2 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma2
```

```{r}
pv2 <- plotMarkers(seMarker = markerTest2, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv2
```

## Three subcluster analysis by PeakMatrix

### Marker Identification 
```{r Marker gene identification using gene scores, echo=TRUE, message=FALSE, cache=FALSE, results='hide'}
table(projStriata5$Clusters4)
markersGS <- getMarkerFeatures(
    ArchRProj = projStriata5, 
    useMatrix = "PeakMatrix", 
    groupBy = "Clusters4",
    bias = c("TSSEnrichment", "log10(nFrags)"),
    testMethod = "wilcoxon", 
    threads = 1
)
```

```{r Marker gene statistical and expression cutoff, eval=TRUE}
markerList1 <- getMarkers(markersGS, cutOff = "FDR <= 0.01 & Log2FC >= .5")
markerList1$C1
write.table(as.data.frame(markerList1),file="./NeuronSubset/markerlist-byPeakMatrix-neurons-threeclusters.csv", quote = F, sep = ",", row.names = F)
```

### Pairwise Testing for the three subclusters under .8 resolution
#### C1 Mix vs Ctrl

```{r}
clusterxtrt <- paste0(projStriata5$Clusters4, "_", projStriata5$Treatment)
projStriata5$clusterxtrt <- clusterxtrt
markerTest6 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C1_Mix",
  bgdGroups = "C1_Ctrl"
)
```


```{r}
pma6 <- plotMarkers(seMarker = markerTest6, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma6
```

```{r}
pv6 <- plotMarkers(seMarker = markerTest6, name = "C1_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv6
```

```{r}
plotPDF(pma6, pv6, name = "C1-Mix-vs-Ctrl-PeakMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C2 Mix vs Ctrl

```{r}
markerTest7 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C2_Mix",
  bgdGroups = "C2_Ctrl"
)
```

```{r}
pma7 <- plotMarkers(seMarker = markerTest7, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma7
```

```{r}
pv7 <- plotMarkers(seMarker = markerTest7, name = "C2_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv7
```

```{r}
plotPDF(pma7, pv7, name = "C2-Mix-vs-Ctrl-PeakMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

#### C3 Mix vs Ctrl analysis

```{r}
markerTest8 <- getMarkerFeatures(
  ArchRProj = projStriata5, 
  useMatrix = "PeakMatrix",
  groupBy = "clusterxtrt",
  testMethod = "wilcoxon",
  bias = c("TSSEnrichment", "log10(nFrags)"),
  useGroups = "C3_Mix",
  bgdGroups = "C3_Ctrl"
)
```

```{r}
pma8 <- plotMarkers(seMarker = markerTest8, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "MA")
pma8
```

```{r}
pv8 <- plotMarkers(seMarker = markerTest8, name = "C3_Mix", cutOff = "FDR <= 0.1 & abs(Log2FC) >= .5", plotAs = "Volcano")
pv8
```

```{r}
plotPDF(pma8, pv8, name = "C3-Mix-vs-Ctrl-PeakMatrix-Markers-MA-Volcano-threesubclusters", width = 5, height = 5, ArchRProj = projStriata5, addDOC = FALSE)
```

## Save ArchR Projects

```{r}
saveArchRProject(ArchRProj = projStriata4, outputDirectory = "Save-ProjStriata4/", load = FALSE)
saveArchRProject(ArchRProj = projStriata5, outputDirectory = "NeuronSubset/", load = FALSE)
```